---
title: "Text mining features in R"
author: "SED/JAK"
date: "31 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

  Data mining has to do with the discovery of useful, valid, unexpected, and understandable knowledge from data. One of the most important distinguishing issues in data mining is size. the amount of data available for exploration has increased exponentially. This poses difficult challenges for the standard data analysis disciplines: One has to consider issues like computational efficiency, limited memory resources, interfaces to databases, etc. Other key distinguishing features are the diversity of data sources that
one frequently encounters in data mining projects, as well as the diversity of data types
(text, sound, video, etc.). All these issues turn data mining into a highly interdisciplinary
subject involving not only typical data analysts but also people working with databases,
data visualization on high dimensions, etc.

# R packages for text mining 
There is a wide range of packages available in R for natural language processing 
Some of them are as follows
 # tm
*tm* package provides some powerful functions which will aid in text-processinf step. It has methods for importing data, handlin corpus, metadat, management, creation of term document matrices and proparocessing methods. 
For transformation of text, there are methods such as stop-word removal, stemming, whitespace removal and so on, *tm* provides functions tm_map, content_transformer, tolowe, stopwords.
## stop-word removal
```{r tm, echo=TRUE}
library(tm)
text <- 'Fully furnished ready to move-In 2bhk in a 3 storeyed private apartment located in ulloor bahsi nagar,kochulloor(best##$//). Residential locality.Karunya residence association
Accessibility-450 m to nh47, 2 kms to byepass and very proximate to medical college,kims hospital and other educational institutions.5 kms to technopark campus.
Occupied only for 2 years and very well maintained. No wall sharing with two covered balconies. Borewell and corporation water connection'

corpus <- VCorpus(VectorSource(text))
corpus <- tm_map(corpus, removeWords, stopwords())
corpus
```

## stop-word removal


For managing documents using the tm package, we create a corpus which is a collection of text documents. There are two types of implementation, volatile corpus(VCorpus) and permanent corpus(PCropus).
 
# Advantage
Taking advantage of the highly flexible database interfaces availablein R,

# Limitations
R has limitations with handling enormous datasets because all computation is carried out in the main memory of the computer. This does not mean that you will not be able to handle these problems. 

